\LARGE \bf ***

### 2020-08-02 icra-2021.tex
updated equation 8 with characteristic time, updated matlab script
updated some formulas (for instance 13 was wrong...)

The non-linear model in Equation~(\ref{eqq:6}) can be expressed using an equivalent time-varying state-space model in the following form
\begin{equation}\label{eqq:7}\begin{cases}
  \dot{\mathbf{q}}(t)&=A\mathbf{q}(t)+B\mathbf{u}(t)+w(t)\\
  y(t)&=C\mathbf{q}(t)+v(t)
\end{cases},\end{equation}
where $y(t)\in\mathbb{R}_{\geq 0}$ is the energy evolution of the system being controlled, $w(t)$ the same process noise of the system in Equation~(\ref{eqq:1}), and $v(t)\in\mathbb{R}_{\geq 0}$ the measurement noise. The control $\mathbf{u}$ along with the input matrix $B$ are defined subsequently. The state $\mathbf{q}$ represents the evolution of the Fourier series coefficients in time, which can be expressed along with the state transition matrix, and the output matrix
\begin{equation}\begin{split}
  \mathbf{q}(t)&=\left[\begin{array}{ccccccc}
    a_0 & \vline & a_1 & b_1 & \cdots & a_r & b_r
  \end{array}\right]^T,\\
  A&=\left[\begin{array}{ccccc}
    1          & \vline & \mathbf{0} & \cdots & \mathbf{0} \\\hline
    \mathbf{0} & \vline & A_1        & \cdots & \mathbf{0} \\
    \vdots     & \vline & \vdots     & \ddots & \vdots     \\
    \mathbf{0} & \vline & \mathbf{0} & \cdots & A_r 
  \end{array}\right],\,A_n=\begin{bmatrix}0 & n \\ -n^2 & 0\end{bmatrix},\\
  C&=\left[\begin{array}{ccccccc}
    1 & \vline & 1 & 0 & \cdots & 1 & 0
  \end{array}\right],
\end{split}\end{equation}
where $\mathbf{q}(t)\in\mathbb{R}^j$ given $j:=2r+1$, $A\in\mathbb{R}^{j\times j}$ is the state transmission matrix, and $C\in\mathbb{R}^j$ is the output matrix. Furthermore, the first row and column of the matrix $A$ contain zeros row vectors and column vectors respectively.

@@

The estimation of the state and the update of the predicted output is done using
\begin{subequations}\label{eqq:11}\begin{align}
  K_k&=(CP_{k+1}^-C^T+R)^{-1}(P_{k+1}^-C^T),\\
  \hat{\mathbf{q}}_{k+1}&=\hat{\mathbf{q}}_{k+1}^-+K_k(y_k-C\hat{\mathbf{q}}_{k+1}^-),\label{eqq:11b}\\
  P_{k+1}&=(I-K_kC)P_{k+1}^-,\\
  \hat{y}_k&=C\hat{\mathbf{q}}_{k+1},\label{eqq:11d}
\end{align}
\end{subequations}
where $K_k\in\mathbb{R}^j$ is the gain of the Kalman filter, and $I$ the identity matrix. The noise covariance matrices $Q\in\mathbb{R}^{j\times j},R\in\mathbb{R}$ indicates the process noise and sensor noise covariance respectively, and $\hat{y}_k\in\mathbb{R}_{\geq 0}$ is the estimated energy.

@@

Suppose the system is composed of $\sigma$ computationally expensive ROS nodes. Let us define the computational control action
\begin{equation}\label{eqq:12}
  \mathcal{C}_k:=\left\{u:u\in\text{QoS}_n(k)\,\forall\,n\in\{0,\dots,\sigma\}\right\},
\end{equation}
where $\text{QoS}_n(t):\mathbb{Z}_{\geq 0}\rightarrow\mathbb{Z}_{\geq 0}$ returns the $n$-th QoS value at time $t$, and $\mathcal{C}_k\in\mathbb{Z}_{\geq 0}^\sigma$ the set of $\sigma$ QoS values the system is composed of at time $k$. Let us further define $g:\mathbb{Z}_{\geq 0}\times\mathbb{Z}_{\geq 0}\rightarrow\mathbb{R}_{\geq 0}$ as the instantaneous energy value obtained interrogating \powprof{}. The computational energy component can be described
\begin{equation}\begin{split}
  g(\mathcal{C}_{k})&:=\{g\left(0,\text{QoS}_0(k)\right),\dots,g\left(\sigma,\text{QoS}_\sigma(k)\right)\},\\
  y_c(t)&=\sum_{x\in g\left(\mathcal{C}_{\ceil{t}}\right)}{x},
\end{split}\end{equation}
where $\ceil{\cdot}$ is the ceiling function that returns the least integer greater than or equal to the argument.

@@

The mechanical and computational control actions, $\mathcal{C}$ and $\mathcal{M}$ defined in Equation~(\ref{eqq:12})~and~(\ref{eqq:14}), are incorporated in the system in Equation~(\ref{eqq:9b}) using the input matrix
\begin{equation}\begin{split}
  \mathbf{u}_k&=\left[\begin{array}{cc}
    g\left(\mathcal{C}_k\right) & \mathcal{M}_k
  \end{array}\right]^T,\\
  B&=\left[\begin{array}{ccccccc}
    1 & \cdots & 1 & \vline & 0 & \cdots & 0\\\hline
    0 & \cdots & 0 & \vline & 0 & \cdots & 0\\
    \vdots & \ddots & \vdots & \vline & \vdots & \ddots & \vdots\\
    0 & \cdots & 0 & \vline & 0 & \cdots & 0
  \end{array}\right],
\end{split}
\end{equation}
where $\mathbf{u}_k\in\mathbb{R}^l$ is the control given $l:=\sigma+\rho$, and $B\in\mathbb{R}^{j\times l}$ is the input matrix from Equation~(\ref{eqq:7})~and~(\ref{eqq:9b}). Moreover, the first $\sigma$ columns in the first row of the input matrix are $1$, while all the other items are $0$. This adds the computational model component to the energy evolution in the system in Equation~(\ref{eqq:9b}). The energy due to the change of explicit trajectory equation parameters is not directly added to the system, which however will update the reading from the sensors in Equation~(\ref{eqq:11b}) and thus adjust the energy evolution accordingly.

>>>>

The non-linear model in Equation~(\ref{eqq:6}) can be expressed using an equivalent time-varying state-space model in the following form
\begin{equation}\label{eqq:7}\begin{cases}
  \dot{\mathbf{q}}(t)&=A\mathbf{q}(t)+B\mathbf{u}(t)+w(t)\\
  y(t)&=C\mathbf{q}(t)+v(t)
\end{cases},\end{equation}
where $y(t)\in\mathbb{R}_{\geq 0}$ is the energy evolution of the system being controlled, $w(t)$ the same process noise of the system in Equation~(\ref{eqq:1}), and $v(t)\in\mathbb{R}_{\geq 0}$ the measurement noise. The control $\mathbf{u}$ along with the input matrix $B$ are defined subsequently. The state $\mathbf{q}$ represents the evolution of the Fourier series coefficients in time, which can be expressed along with the state transition matrix, and the output matrix
\begin{equation}\begin{split}
  \mathbf{q}(t)&=\left[\begin{array}{ccccccc}
    a_0 & \vline & a_1 & b_1 & \cdots & a_r & b_r
  \end{array}\right]^T,\\
  A&=\left[\begin{array}{ccccc}
    1          & \vline & \mathbf{0} & \cdots & \mathbf{0} \\\hline
    \mathbf{0} & \vline & A_1        & \cdots & \mathbf{0} \\
    \vdots     & \vline & \vdots     & \ddots & \vdots     \\
    \mathbf{0} & \vline & \mathbf{0} & \cdots & A_r 
  \end{array}\right],\,A_n=\begin{bmatrix}0 & \frac{n}{\xi} \\ -\frac{n^2}{\xi^2} & 0\end{bmatrix},\\
  C&=\left[\begin{array}{ccccccc}
    1 & \vline & 1 & 0 & \cdots & 1 & 0
  \end{array}\right],
\end{split}\end{equation}
where $\mathbf{q}(t)\in\mathbb{R}^j$ given $j:=2r+1$, $A\in\mathbb{R}^{j\times j}$ is the state transmission matrix, and $C\in\mathbb{R}^j$ is the output matrix. Furthermore, the first row and column of the matrix $A$ contain zeros row vectors and column vectors respectively.

@@

The estimation of the state and the update of the predicted output is done using
\begin{subequations}\label{eqq:11}\begin{align}
  K_k&=(CP_{k+1}^-C^T+R)^{-1}(P_{k+1}^-C^T),\\
  \hat{\mathbf{q}}_{k+1}&=\hat{\mathbf{q}}_{k+1}^-+K_k(y_k^s+y_k^c-C\hat{\mathbf{q}}_{k+1}^-),\label{eqq:11b}\\
  P_{k+1}&=(I-K_kC)P_{k+1}^-,\\
  \hat{y}_k&=C\hat{\mathbf{q}}_{k+1},\label{eqq:11d}
\end{align}
\end{subequations}
where $K_k\in\mathbb{R}^j$ is the gain of the Kalman filter, and $I$ the identity matrix. $y_k^s,y_k^c$ are the energy readings: $y_k^s$ the flight controller sensor, i.e., the energy needed for the actuation, and $y_k^c$ the energy of a given software configuration described in Equation~(\ref{eqq:13}) later in this section. The noise covariance matrices $Q\in\mathbb{R}^{j\times j},R\in\mathbb{R}$ indicates the process noise and sensor noise covariance respectively, and $\hat{y}_k\in\mathbb{R}_{\geq 0}$ is the estimated energy.

@@

Suppose the system is composed of $\sigma$ computationally expensive ROS nodes. Let us define the computational control action
\begin{equation}\label{eqq:12}
  \mathcal{C}_k:=\left\{u:u\in\text{QoS}_n(k)\,\forall\,n\in\{0,\dots,\sigma\}\right\},
\end{equation}
where $\text{QoS}_n(t):\mathbb{Z}_{\geq 0}\rightarrow\mathbb{Z}_{\geq 0}$ returns the $n$-th QoS value at time $t$, and $\mathcal{C}_k\in\mathbb{Z}_{\geq 0}^\sigma$ the set of $\sigma$ QoS values the system is composed of at time $k$. Let us further define $g:\mathbb{Z}_{\geq 0}\times\mathbb{Z}_{\geq 0}\rightarrow\mathbb{R}_{\geq 0}$ as the instantaneous energy value obtained interrogating \powprof{}. The computational energy component can be defined
\begin{equation}\label{eqq:13}\begin{split}
  y_k^c:&=g\left(\text{QoS}_0\left(k\right),\dots,\text{QoS}_\sigma\left(k\right)\right)=g\left(\mathcal{C}_{k}\right).\\
\end{split}\end{equation}

@@

The mechanical and computational control actions, $\mathcal{C}$ and $\mathcal{M}$ defined in Equation~(\ref{eqq:12})~and~(\ref{eqq:14}), are incorporated in the system in Equation~(\ref{eqq:9b}) using the input matrix
\begin{equation}\begin{split}
  \mathbf{u}_k&=\left[\begin{array}{cc}
    g\left(\mathcal{C}_k\right) & \mathcal{M}_k
  \end{array}\right]^T,\\
  B&=\left[\begin{array}{ccccccc}
    1 & \vline & 0 & \cdots & 0\\\hline
    0 & \vline & 0 & \cdots & 0\\
    \vdots & \vline & \vdots & \ddots & \vdots\\
    0 & \vline & 0 & \cdots & 0
  \end{array}\right],
\end{split}
\end{equation}
where $\mathbf{u}_k\in\mathbb{R}^l$ is the control given $l:=1+\rho$, and $B\in\mathbb{R}^{j\times l}$ is the input matrix from Equation~(\ref{eqq:7})~and~(\ref{eqq:9b}). Moreover, the first column in the first row of the input matrix is $1$, while all the other items are $0$. This adds the computational model component to the energy evolution in the system in Equation~(\ref{eqq:9b}). The energy due to the change of explicit trajectory equation parameters is not directly added to the system, which however will update the reading from the sensors in Equation~(\ref{eqq:11b}) and thus adjust the energy evolution accordingly.
